Isolator: accurate and consistent analysis of isoform-level expression in RNA-Seq experiments

### 2016-06-01 paper.tex
NextSeq not HiSeq was used in rhemac data.

RNA-Seq reads become more informative with length and quantity. We
compared data from the same sample sequenced twice, once with 300nt
paired-end reads on a MiSeq sequencer and again with 100nt paired-end
reads using a HiSeq 2000, yielding approximately 4.5 million and 11
million reads, respectively. To elucidate the effect of deeper
sequencing, we sampled without replacement smaller subsets of the 11
million HiSeq 2000 reads and measured correlation between estimates made using
these subsamples with estimates from the MiSeq data (Figure \ref{fig:rhemac}).

@@

\begin{figure}
\includegraphics[width=0.5\textwidth]{rhemac-figure.pdf}
\caption{Proportionality correlation between estimates from 4.5 million 300nt
MiSeq reads and progressively larger numbers of HiSeq 2000 reads. For clarity,
correlations for RSEM/PM are excluded as they were much lower than the other
methods.}
\label{fig:rhemac}
\end{figure}

>>>>

RNA-Seq reads become more informative with length and quantity. We
compared data from the same sample sequenced twice, once with 300nt
paired-end reads on a MiSeq sequencer and again with 100nt paired-end
reads using a NextSeq 500, yielding approximately 4.5 million and 11
million reads, respectively. To elucidate the effect of deeper
sequencing, we sampled without replacement smaller subsets of the 11
million NextSeq 500 reads and measured correlation between estimates made using
these subsamples with estimates from the MiSeq data (Figure \ref{fig:rhemac}).

@@

\begin{figure}
\includegraphics[width=0.5\textwidth]{rhemac-figure.pdf}
\caption{Proportionality correlation between estimates from 4.5 million 300nt
MiSeq reads and progressively larger numbers of NextSeq 500 reads. For clarity,
correlations for RSEM/PM are excluded as they were much lower than the other
methods.}
\label{fig:rhemac}
\end{figure}
